Creating the ``r params$package_name`` R package

### 2025-10-07 create-FSHybridPLS.Rmd
remove bootstrap code

```{r}
#' @import funData
NULL

@@

```{r}
#' Multivariate functional principal component analysis for functions on
#' different (dimensional) domains
#' This function calculates a multivariate functional principal component
#' analysis (MFPCA) based on i.i.d. observations \eqn{x_1, \ldots, x_N} of a
#' multivariate functional data-generating process \eqn{X = (X^{(1)}, \ldots
#' X^{(p)})}{X = X^(1), \ldots, X^(p)} with elements \eqn{X^{(j)} \in
#' L^2(\mathcal{T}_j)}{X^(j) in L^2(calT_j)} defined on a domain
#' \eqn{\mathcal{T}_j \subset IR^{d_j}}{calT_j of IR^{d_j}}. In particular, the
#' elements can be defined on different (dimensional) domains. The results
#' contain the mean function, the estimated multivariate functional principal
#' components \eqn{\hat \psi_1, \ldots, \hat \psi_M} (having the same structure
#' as \eqn{x_i}), the associated eigenvalues \eqn{\hat \nu_1 \geq \ldots \geq
#' \hat \nu_M > 0} and the individual scores \eqn{\hat \rho_{im} =
#' \widehat{<x_i, \psi_m>}}{\hat \rho_{im} = \hat{<x_i, \psi_m>}}. Moreover,
#' estimated trajectories for each observation based on the truncated
#' Karhunen-Loeve representation \deqn{\hat x_i = \sum_{m = 1}^M \hat \rho_{im}
#' \hat \psi_m}{\hat x_i = \sum_{m = 1}^M \hat \rho_{im} \hat \psi_m} are given
#' if desired (\code{fit = TRUE}). The implementation of the observations
#' \eqn{x_i = (x_i^{(1)}, \ldots , x_i^{(p)}),~ i = 1 , \ldots, N}{x_i =
#' (x_i^(1), \ldots , x_i^(p)), i = 1 , \ldots, N}, the mean function and
#' \psi_M} uses the \code{\link[funData]{multiFunData}} class, which is defined
#' in the package \pkg{funData}.
#' \subsection{Weighted MFPCA}{If the elements vary considerably in domain,
#' range or variation, a weight vector \eqn{w_1 , \ldots, w_p} can be supplied
#' and the MFPCA is based on the weighted scalar product \deqn{<<f,g>>_w =
#' \sum_{j = 1}^p w_j \int_{\mathcal{T}_j} f^{(j)}(t) g^{(j)}(t) \mathrm{d}
#' t}{<<f,g>>_w = \sum_{j = 1}^p w_j \int_\calT_j f^(j)(t) g^(j)(t) d t} and the
#' corresponding weighted covariance operator \eqn{\Gamma_w}.}
#' \subsection{Bootstrap}{If \code{bootstrap = TRUE}, pointwise bootstrap
#' confidence bands are generated for the multivariate eigenvalues \eqn{\hat
#' \nu_1, \ldots, \hat \nu_M } as well as for multivariate functional principal
#' components \eqn{\hat \psi_1, \ldots, \hat \psi_M}{\hat \psi_1, \ldots, \hat
#' \psi_M}. The parameter \code{nBootstrap} gives the number of bootstrap
#' iterations. In each iteration, the observations are resampled on the level of
#' (multivariate) functions and the whole MFPCA is recalculated. In particular,
#' if the univariate basis depends on the data (FPCA approaches), basis
#' functions and scores are both re-estimated. If the basis functions are fixed
#' (e.g. splines), the scores from the original estimate are used to speed up
#' the calculations. The confidence bands for the eigenfunctions are calculated
#' separately for each element as pointwise percentile bootstrap confidence
#' intervals. Analogously, the confidence bands for the eigenvalues are also
#' percentile bootstrap confidence bands. The significance level(s) can be
#' defined by the \code{bootstrapAlpha} parameter, which defaults to 5\%. As a
#' result, the \code{MFPCA} function returns a list \code{CI} of the same length
#' as \code{bootstrapAlpha}, containing the lower and upper bounds of the
#' confidence bands for the principal components as \code{multiFunData} objects
#' of the same structure as \code{mFData}. The confidence bands for the
#' eigenvalues are returned in a list \code{CIvalues}, containing the upper and
#' lower bounds for each significance level.}

@@

#' \subsection{Univariate Expansions}{The multivariate functional principal
#' component analysis relies on a univariate basis expansion for each element
#' \eqn{X^{(j)}}{X^(j)}. The univariate basis representation is calculated using
#' the \code{\link{univDecomp}} function, that passes the univariate functional
#' observations and optional parameters to the specific function. The univariate
#' decompositions are specified via the \code{uniExpansions} argument in the
#' \code{MFPCA} function. It is a list of the same length as the \code{mFData}
#' object, i.e. having one entry for each element of the multivariate functional
#' data. For each element, \code{uniExpansion} must specify at least the type of
#' basis functions to use. Additionally, one may add further parameters. The
#' following basis representations are supported: \itemize{\item Given basis

@@

#' same domain as \code{mFData}, containing the given basis functions. The

@@

#' supplied, they are calculated using the given basis functions. The parameter

@@

#' @examples
#' oldPar <- par(no.readonly = TRUE)
#' set.seed(1)
#' ### simulate data (one-dimensional domains)
#' sim <-  simMultiFunData(type = "split", argvals = list(seq(0,1,0.01), seq(-0.5,0.5,0.02)),
#'                         M = 5, eFunType = "Poly", eValType = "linear", N = 100)
#' # MFPCA based on univariate FPCA
#' uFPCA <- MFPCA(sim$simData, M = 5, uniExpansions = list(list(type = "uFPCA"),

@@

```{r}
#'
MFPCA <- function(mFData, mFData_predict, M, uniExpansions, weights = rep(1, length(mFData)), fit = FALSE, approx.eigen = FALSE,
                  bootstrap = FALSE, nBootstrap = NULL, bootstrapAlpha = 0.05, bootstrapStrat = NULL,
                  verbose = options()$verbose)
{
  if(! inherits(mFData, "multiFunData"))
    stop("Parameter 'mFData' must be passed as a multiFunData object.")

  # calculate univariate basis expansion for all components
  uniBasis <- mapply(
    function(expansion, data, data_predict){
      do.call(univDecomp, c(
        list(funDataObject = data, funDataObject_predict = data_predict),
        expansion)
        )
      },
    expansion = uniExpansions,
    data = mFData,
    data_predict = mFData_predict,
    SIMPLIFY = FALSE
    )
########### modified by Jongmin Mun #############################

  # bootstrap for eigenfunctions
  if(bootstrap)
  {
    if(verbose)
      cat("Bootstrapping results:\n")

    booteFuns <- vector("list", p)

    for(j in seq_len(p))
      booteFuns[[j]] <- array(NA, dim  = c(nBootstrap, M, vapply(mFData[[j]]@argvals, FUN = length, FUN.VALUE = 0)))

    booteVals <- matrix(NA, nrow = nBootstrap, ncol = M)

    for(n in seq_len(nBootstrap))
    {
      if(verbose)
      {
        if(n %% 10 == 0)
          cat("\t n = ", n, " (", format(Sys.time(), "%T"), ")\n", sep = "")
      }

      if(is.null(bootstrapStrat))
        bootObs <- sample(N, replace = TRUE)
      else
        bootObs <- stratSample(bootstrapStrat)

      bootBasis <- vector("list", p)

      for(j in seq_len(p))
      {
        if(!is.null(uniBasis[[j]]$functions)) # re-estimate scores AND functions
        {
          bootBasis[[j]] <- do.call(univDecomp, c(list(funDataObject = (mFData[bootObs])[[j]]), uniExpansions[[j]]))

          # recalculate Bchol if necessary
          if(!bootBasis[[j]]$ortho)
            Bchol[[j]] <- Matrix::chol(bootBasis[[j]]$B)
        }
        else # resample scores (functions are given and scores can simply be resampled)
          bootBasis[[j]] <- list(scores = uniBasis[[j]]$scores[bootObs, ], B = uniBasis[[j]]$B, ortho = uniBasis[[j]]$ortho, functions = uniBasis[[j]]$functions,
                                 settings = uniBasis[[j]]$settings)
      }

      npcBoot <- vapply(bootBasis, function(x){dim(x$scores)[2]}, FUN.VALUE = 0) # get number of univariate basis functions

      if(M > sum(npcBoot))
        stop("Function MFPCA (bootstrap): total number of univariate basis functions must be greater or equal M!")

      # calculate MFPCA for bootstrap sample (Bchol has been updated for UMPCA)
      bootMFPCA <- calcMFPCA(N = N, p = p, Bchol = Bchol, M = M, type = type, weights = weights,
                             npc = npcBoot, argvals = mArgvals, uniBasis = bootBasis, fit = FALSE, approx.eigen = approx.eigen)

      # save eigenvalues
      booteVals[n,] <- bootMFPCA$values

      # flip bootstrap estimates if necessary
      tmpFuns <- flipFuns(res$functions, bootMFPCA$functions)

      # save in booteFuns
      for(j in seq_len(p))
      {
        if(dimSupp[j] == 1)
          booteFuns[[j]][n,,] <- tmpFuns[[j]]@X
        if(dimSupp[j] == 2)
          booteFuns[[j]][n,,,] <- tmpFuns[[j]]@X
        if(dimSupp[j] == 3)
          booteFuns[[j]][n,,,,] <- tmpFuns[[j]]@X
      }
    }

    CIvalues <- vector("list", length(bootstrapAlpha))
    CI <- vector("list", length(bootstrapAlpha))

    for(alpha in seq_len(length(bootstrapAlpha)))
    {
      if(verbose)
        cat("Calculating bootstrap quantiles for alpha = ", bootstrapAlpha[alpha], " (", format(Sys.time(), "%T"), ")\n", sep = "")

      CIvalues[[alpha]]$lower <- apply(booteVals, 2, quantile, bootstrapAlpha[alpha]/2)
      CIvalues[[alpha]]$upper <-  apply(booteVals, 2, quantile, 1 - bootstrapAlpha[alpha]/2)
      names(CIvalues)[alpha] <- paste("alpha", bootstrapAlpha[alpha], sep = "_")

      bootCI_lower <- bootCI_upper <-  vector("list", p)
      for(j in seq_len(p))
      {
        bootCI_lower[[j]] <- funData(mFData[[j]]@argvals, apply(booteFuns[[j]], 2:length(dim(booteFuns[[j]])),
                                                                quantile, bootstrapAlpha[alpha]/2))
        bootCI_upper[[j]] <- funData(mFData[[j]]@argvals, apply(booteFuns[[j]],  2:length(dim(booteFuns[[j]])),
                                                                quantile, 1 - bootstrapAlpha[alpha]/2))
      }

      CI[[alpha]]$lower <- multiFunData(bootCI_lower)
      CI[[alpha]]$upper <- multiFunData(bootCI_upper)

      names(CI)[alpha] <- paste("alpha", bootstrapAlpha[alpha], sep = "_")
    }

    res$CIvalues <- CIvalues

    res$CI <- CI
  }
  if(type[1] == "uFPCA"){
    scores.pred<-calcMFPCA_predict(N = nObs(mFData_predict),
                      p = p,
                      M = M,
                      weights = weights,
                      npc = npc,
                      uniBasis = uniBasis,
                      normFactors = res$normFactors,
                      vectors_train=res$vectors,
                      values_train=res$values
    )
  }
  res$scores.pred <- scores.pred

  class(res) <- "MFPCAfit"
    return(res)
}
```

>>>>

functions in MFPCA packages use an internal function calcBasisIntegrals. Somehow, this function did not work well on our simulations setting. Thus we modify the codes 
```{r}
#' @import funData
NULL

@@

###   Multivariate functional principal component analysis for functions on different (dimensional) domains

- This function calculates a multivariate functional principal component analysis (MFPCA) based on i.i.d. observations $x_1, \ldots, x_N$ of a multivariate functional data-generating process $X = (X^{(1)}, \ldots  X^{(p)})}{X = X^(1), \ldots, X^(p)$ with elements $X^{(j)} \in L^2(\mathcal{T}_j)}{X^(j) in L^2(calT_j)$ defined on a domain $\mathcal{T}_j \subset IR^{d_j}}{calT_j of IR^{d_j}$.
- In particular, the elements can be defined on different (dimensional) domains.
- The results contain the mean function, the estimated multivariate functional principal components \eqn{\hat \psi_1, \ldots, \hat \psi_M} (having the same structure as $x_i$), the associated eigenvalues $\hat \nu_1 \geq \ldots \geq \hat \nu_M > 0$ and the individual scores \eqn{\hat \rho_{im} = \widehat{<x_i, \psi_m>}}{\hat \rho_{im} = \hat{<x_i, \psi_m>}}.

@@

- Univariate Expansions
  - The multivariate functional principal component analysis relies on a univariate basis expansion for each element $X^{(j)}$.
  - The univariate basis representation is calculated using the univDecomp function, that passes the univariate functional observations and optional parameters to the specific function.
  - The univariate decompositions are specified via the uniExpansions argument in the MFPCA function.
  - It is a list of the same length as the mFData object, i.e. having one entry for each element of the multivariate functional data.
  - For each element, uniExpansion must specify at least the type of basis functions to use.
  - Additionally, one may add further parameters.
  - The following basis representations are supported: \itemize{\item Given basis

@@

#' same domain as \code{mFData}, containing the given basis functions. 
The

@@

#' supplied, they are calculated using the given basis functions.
The parameter

@@

MFPCA <- function(mFData, mFData_predict, M, uniExpansions, weights = rep(1, length(mFData)), fit = FALSE, approx.eigen = FALSE,
                  bootstrap = FALSE, nBootstrap = NULL, bootstrapAlpha = 0.05, bootstrapStrat = NULL,
                  verbose = options()$verbose)
{
  if(! inherits(mFData, "multiFunData"))
    stop("Parameter 'mFData' must be passed as a multiFunData object.")

########### modified by Jongmin Mun #############################
  # calculate univariate basis expansion for all components
  uniBasis <- mapply(
    function(expansion, data, data_predict){
      do.call(univDecomp, c(
        list(funDataObject = data, funDataObject_predict = data_predict),
        expansion)
        )
      },
    expansion = uniExpansions,
    data = mFData,
    data_predict = mFData_predict,
    SIMPLIFY = FALSE
    )
########### modified by Jongmin Mun #############################

  if(type[1] == "uFPCA"){
    scores.pred<-calcMFPCA_predict(N = nObs(mFData_predict),
                      p = p,
                      M = M,
                      weights = weights,
                      npc = npc,
                      uniBasis = uniBasis,
                      normFactors = res$normFactors,
                      vectors_train=res$vectors,
                      values_train=res$values
    )
  }
  res$scores.pred <- scores.pred

  class(res) <- "MFPCAfit"
    return(res)
}

```{r}
#' @examples
#' oldPar <- par(no.readonly = TRUE)
#'
#' set.seed(1)
#'
#' ### simulate data (one-dimensional domains)
#' sim <-  simMultiFunData(type = "split", argvals = list(seq(0,1,0.01), seq(-0.5,0.5,0.02)),
#'                         M = 5, eFunType = "Poly", eValType = "linear", N = 100)
#'
#' # MFPCA based on univariate FPCA
#' uFPCA <- MFPCA(sim$simData, M = 5, uniExpansions = list(list(type = "uFPCA"),
#'                                                                   list(type = "uFPCA")))

@@

#' Internal function that implements the MFPCA algorithm for given univariate decompositions
#'
#' @param N Number of observations.
#' @param p Number of elements in multivariate functional data.
#' @param Bchol Cholesky decomposition of B = block diagonal of Cholesky decompositions.
#' @param M The number of multivariate functional principal components to
#'   calculate.
#' @param type Vector of univariate decompositions to use.
#' @param weights Vector of weights.
#' @param npc Vector giving the number of univariate basis functions used.
#' @param argvals List of argument values for each of the univariate basis functions.
#' @param uniBasis List of univariate basis functions.
#' @param fit Logical. If \code{TRUE}, a truncated multivariate Karhunen-Loeve
#'   representation for the data is calculated based on the estimated scores and
#'   eigenfunctions.
#' @param approx.eigen Logical. If \code{TRUE}, the eigenanalysis problem for
#'   the estimated covariance matrix is solved approximately using the
#'   \pkg{irlba} package, which is much faster. If the number \code{M} of
#'   eigenvalues to calculate is high with respect to the number of observations
#'   in \code{mFData} or the number of estimated univariate eigenfunctions, the
#'   approximation may be inappropriate. In this case, approx.eigen is set to
#'   \code{FALSE} and the function throws a warning. Defaults to \code{FALSE}.
#'
#' @return A list containing the following
#'   components: \item{values}{A vector of estimated eigenvalues \eqn{\hat \nu_1
#'   , \ldots , \hat \nu_M}.} \item{functions}{A
#'   \code{\link[funData]{multiFunData}} object containing the estimated
#'   multivariate functional principal components \eqn{\hat \psi_1, \ldots, \hat
#'   \psi_M}.} \item{scores}{ A matrix of dimension \code{N x M} containing the
#'   estimated scores \eqn{\hat \rho_{im}}.} \item{vectors}{A matrix
#'   representing the eigenvectors associated with the combined univariate score
#'   vectors. This might be helpful for calculating predictions.}
#'   \item{normFactors}{The normalizing factors used for calculating the
#'   multivariate eigenfunctions and scores. This might be helpful when
#'   calculation predictions.} \item{meanFunction}{A multivariate functional
#'   data object, corresponding to the mean function. The MFPCA is applied to
#'   the de-meaned functions in \code{mFData}.}\item{fit}{A
#'   \code{\link[funData]{multiFunData}} object containing estimated
#'   trajectories for each observation based on the truncated Karhunen-Loeve
#'   representation and the estimated scores and eigenfunctions.}
#'
#' @importFrom stats cov
#' @importFrom Matrix t
#' @importFrom foreach foreach
#' @importFrom irlba irlba
#'
#' @keywords internal
calcMFPCA <- function(N, p, Bchol, M, type, weights, npc, argvals, uniBasis, fit = FALSE, approx.eigen = FALSE)
{
  # combine all scores
  allScores <- foreach::foreach(j = seq_len(p), .combine = "cbind")%do%{uniBasis[[j]]$scores}
